### 2024-06-19 manuscript.Rmd
Update manuscript.Rmd
In this order I find it more coherent
Update manuscript.Rmd
typo? Did not find the other part of the parenthesis
Update manuscript.Rmd
I somehow stumbled over this sentence, not completely sure why. I feel it sounds better with plural instead of singular, as "comparison" somehow implies that there need to be more than one object, but maybe this is just me

The `reproducibleRchunk` package allows users to make computational results in R Markdown documents automatically testable for reproduction (does the same script with the same data produce the same results, e.g. on a different computer and/or later in time) with minimal changes to your workflow.
There is only a single thing users need to change in their Markdown document if they are already using R Markdown: In the first code chunk of their document, load the package and then change the code chunk type from `r` to `reproducibleR` for all code chunks that should be automatically checked for reproducibility.
In `reproducibleR` chunks, all newly declared variables are automatically identified and their contents are stored in a meta data file. 
Furthermore, the code chunk itself (that is, the code syntax) is also fingerprinted and stored, such that later non-reproduction can be traced back to either changes of the code chunk or changes of the computation.
Once a document is reproduced, in R-Markdown-speak _knitted_ again [@yihui2015], all computational results generated in the `reproducibleR` chunks are automatically tested for reproducibility.
The result of the reproduction attempt is displayed in a reproducibility report for each chunk.
Customizations of these reports are possible as we will demonstrate later.
A simple way to assess reproducibility of computational results would be  a bitwise comparison of the entire knitted document (i.e., the resulting HTML, PDF or DOCX file).
Yet, a particular advantage of using `reproducibleR` chunks is that users have a fine-grained control over which stages of a data analysis or any other computation should be checked for reproducibility. 
For example, if there is non-reproducibility, is it due to changes in the data file, during data cleaning or statistical modeling. 
Using `reproducibleRchunks`, users can separately assess the reproducibility of each stage of a given statistical data analysis (or any other computation).
Also, not all elements of a research asset are required to reproduce (such as the current date displayed in a presentation of results).
In the following, we will briefly demonstrate how successful and failed reproduction will be checked and displayed by the package, we will go into details of the mechanics of the package, and discuss potential cases of non-reproducibility and how the package will support researchers in handling these cases.

@@

In the following, we will describe how the package stores, retrieves and compares reproducibility information.
First of all, the package executes `reproducibleR` code chunks just as regular R code chunks.
That is, there are no additional limits imposed on what can be computed and tested for reproducibility.
Once code execution is completed, the package gathers information about all variables that were newly declared in the current chunk. 
The contents of those variables are stored in a separate JSON data file.
JSON is a shorthand for Java Script Object Notation and its main features are that it is an open standard for mapping complex objects to text files with high simplicity and readability for machines and humans [@lennon2009introduction].
The name of the JSON file contains the original Markdown file and the chunk label and always starts with the prefix `repro`). 
That is, if reproducibility information of a chunk labelled `datacleaning` in the file `sem_analysis.Rmd` is stored in a file called _.repro_sem_analysis.Rmd_datacleaning.json_.
Once the document is re-generated and JSON data files exist, their content is checked against the newly computed chunk variables for identity.

@@

Once a document is (re-)generated with reproducibility data present (i.e., reproducibleRchunks with matching JSON files), the package will compare all objects amenable for reproducibility checks.
Identity of original and reproduced results are checked with `identical()` function from R's `base` package, which according to the R documentation is a "safe and reliable way to test two objects (even complex ones) for being exactly identical" (see `?identical` R documentation).
Using exact comparisons of object identity is sometimes more restrictive than one would expect.
This is particularly true for numeric comparisons. 
For example results of numeric computations may be logically equivalent but not bitwise equivalent; in numeric representations, there is sometimes a bit reserved for the sign of a number, thus it can be possible to have -0 and +0, which both are exactly zero in a decimal representation but the binary representations differ.
Numeric representations may also differ up to a given numeric precision, for example, when comparing reproducibility across machines that work with different numerical precision (32bit vs 64bit). To avoid such problems, `reproducibleRchunks` rounds numeric values to a given precision (by default, eight digits)

>>>>

The `reproducibleRchunk` package allows users to make computational results in R Markdown documents automatically testable for reproduction (does the same script with the same data produce the same results, e.g. on a different computer and/or later in time) with minimal changes to your workflow.
There is only a single thing users need to change in their Markdown document if they are already using R Markdown: In the first code chunk of their document, load the package and then change the code chunk type from `r` to `reproducibleR` for all code chunks that should be automatically checked for reproducibility.
In `reproducibleR` chunks, all newly declared variables are automatically identified and their contents are stored in a meta data file. 
Furthermore, the code chunk itself (that is, the code syntax) is also fingerprinted and stored, such that later non-reproduction can be traced back to either changes of the code chunk or changes of the computation.
Once a document is reproduced, in R-Markdown-speak _knitted_ again [@yihui2015], all computational results generated in the `reproducibleR` chunks are automatically tested for reproducibility.
The result of the reproduction attempt is displayed in a reproducibility report for each chunk.
Customizations of these reports are possible as we will demonstrate later.
A simple way to assess reproducibility of computational results would be  a bitwise comparison of the entire knitted document (i.e., the resulting HTML, PDF or DOCX file).
For example, if there is non-reproducibility, is it due to changes in the data file, during data cleaning or statistical modeling. 
Yet, a particular advantage of using `reproducibleR` chunks is that users have a fine-grained control over which stages of a data analysis or any other computation should be checked for reproducibility. 
Using `reproducibleRchunks`, users can separately assess the reproducibility of each stage of a given statistical data analysis (or any other computation).
Also, not all elements of a research asset are required to reproduce (such as the current date displayed in a presentation of results).
In the following, we will briefly demonstrate how successful and failed reproduction will be checked and displayed by the package, we will go into details of the mechanics of the package, and discuss potential cases of non-reproducibility and how the package will support researchers in handling these cases.

@@

In the following, we will describe how the package stores, retrieves and compares reproducibility information.
First of all, the package executes `reproducibleR` code chunks just as regular R code chunks.
That is, there are no additional limits imposed on what can be computed and tested for reproducibility.
Once code execution is completed, the package gathers information about all variables that were newly declared in the current chunk. 
The contents of those variables are stored in a separate JSON data file.
JSON is a shorthand for Java Script Object Notation and its main features are that it is an open standard for mapping complex objects to text files with high simplicity and readability for machines and humans [@lennon2009introduction].
The name of the JSON file contains the original Markdown file and the chunk label and always starts with the prefix `repro`. 
That is, if reproducibility information of a chunk labelled `datacleaning` in the file `sem_analysis.Rmd` is stored in a file called _.repro_sem_analysis.Rmd_datacleaning.json_.
Once the document is re-generated and JSON data files exist, their content is checked against the newly computed chunk variables for identity.

@@

Once a document is (re-)generated with reproducibility data present (i.e., reproducibleRchunks with matching JSON files), the package will compare all objects amenable for reproducibility checks.
Identity of original and reproduced results are checked with `identical()` function from R's `base` package, which according to the R documentation is a "safe and reliable way to test two objects (even complex ones) for being exactly identical" (see `?identical` R documentation).
Using exact comparisons of object identities is sometimes more restrictive than one would expect.
This is particularly true for numeric comparisons. 
For example results of numeric computations may be logically equivalent but not bitwise equivalent; in numeric representations, there is sometimes a bit reserved for the sign of a number, thus it can be possible to have -0 and +0, which both are exactly zero in a decimal representation but the binary representations differ.
Numeric representations may also differ up to a given numeric precision, for example, when comparing reproducibility across machines that work with different numerical precision (32bit vs 64bit). To avoid such problems, `reproducibleRchunks` rounds numeric values to a given precision (by default, eight digits)
